---
title: "RNASeq_analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RNASeq_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basic Default Worflow

```{r setup}
library(RNAseqStat)
results_dir = "test"
```

## run all in one time

`runAll` will run full workflow in default parameters

``` r
runAll(count_data = counts_input, group_list = group_list, 
       test_group = "T", control_group = "C",
       OrgDb = 'org.Hs.eg.db', dir = results_dir)
```

This step contains following 5 steps, more detail parameters can be set in following functions.

### Check your data

This step is useful to quickly check you data. dir Can be any wherr you want to save results file.

```{r eval=FALSE}
pre_check(counts_data = counts_input, group_list = group_list, dir = results_dir)
```

### DEG analysis

DEG analysis will be run by limma edgeR and DESeq2 in this step.

```{r eval=FALSE}
deg_run(counts_input,group_list,test_group = "T", control_group = "C",dir = results_dir)
```

### GO

Enrichment analysis of GO will be done in this Step.

```{r eval=FALSE}
enrichGO_run(DEG_df, x = "log2FoldChange", y = "pvalue", dir = results_dir)
```

### KEGG

Enrichment analysis of KEGG will be done in this Step.

```{r eval=FALSE}
enrichKEGG_run(DEG_df, x = "log2FoldChange", y = "pvalue", dir = results_dir)
```

### GSEA

```{r eval=FALSE}
enrichgesKEGG_run(DEG_df, x = "log2FoldChange", dir = results_dir)
```
